### 2018-04-20 concepts.tex
wording

Finally, we note that this problem is not limited to debugging
nondeterminism/flakiness itself.  In some settings, we have observed
delta-debugging taking a test that had such a high probability of
failure we were unaware it was ``flaky'' (large runs showed there was
indeed a small chance of the test passing) and transforming it into a
test that only failed once in every 10 to 20 executions.
Delta-debugging, without taking potential nondeterminism into account,
can act as a flakiness magnifier, with unfortunate consequences for
debugging.  Multiple evaluations, with replications, are our proposed solution.

>>>>

Finally, we note that this problem is not limited to debugging
nondeterminism/flakiness itself.  In some settings, we have observed
delta-debugging taking a test that had such a high probability of
failure we were unaware it was ``flaky'' (only hundreds of repeated executions showed there was
indeed a small chance of the test passing) and transforming it into a
test that only failed once in every 10 to 20 executions.
Delta-debugging, without taking potential nondeterminism into account,
can act as a flakiness magnifier, with unfortunate consequences for
debugging.  Multiple evaluations, with replications, are our proposed solution.
